---
title: "MSDS 6306_Unit 4 Assignment"
author: "Swee K Chew"
date: "06/07/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1 
### FiveThirtyEight Data 

#### a. Load the "fivethirtyeight" package after the installation
```{r recent_grads1, echo=TRUE}
library(fivethirtyeight)
```

#### b. Assign the 22nd dataset, "college_recent_grads", to an object named "df"
```{r recent_grads2, echo=TRUE}
data(college_recent_grads)
df <- college_recent_grads
```

#### c. URL to the related news story from the a more detailed list of the dataset
```{r recent_grads3, echo=TRUE}
data(package = "fivethirtyeight")
vignette("fivethirtyeight", package = "fivethirtyeight")
```
URL link: https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/


#### d. Dimensions and column names of the data frame, "df"
```{r recent_grads4, echo=TRUE}
dim(df)
colnames(df)
```

## Question 2
### Data Summary

#### a. Column names and counts of columns of the data frame, "df"
```{r recent_grads5, echo=TRUE}
colnames(df)
ncol(df)
```

#### b. Counts of each unique major_category and the frequency in the dataset
```{r recent_grads6, echo=TRUE}
library(plyr)
major_count <- count(df,"major_category")
major_count
```

#### c. Barplot of major_count 
```{r recent_grads7, echo=TRUE}
major_count2 <- table(df$major_category)
par(las=2, mar=c(4,15,4,6))
barplot(major_count2, main = "Numbers of Majors within Each Major Category \nfor Recent College Graduates", xlab = "Numbers of Majors", ylab = "Major Category", xlim = c(0,30), col = "blue", horiz = TRUE) 
```

#### d. Write the "college_recent_grads" dataset to a csv file 
```{r recent_grads8, echo=TRUE}
write.csv(df, file = "college_recent_grads.csv",row.names=FALSE)
```

## Question 3
### CodeBook
#### A repository on GitHub for SMU MSDS Homework

GitHub link: https://github.com/sweechew91/SMU-MSDS-6306


