---
title: "MSDS 6306_Unit 5 Assignment"
author: "Swee K Chew"
date: "06/12/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1 
### Data Munging 

#### a. Import 'yob2016.txt' file and assign the dataset to an object 'df', rename column names
```{r babynames1}
df <- read.table("/Users/swee/Desktop/SMU/Summer 2018/MSDS 6306 - Doing DS/dataset/yob2016.txt", sep= ";", header = TRUE)
colnames(df) <- c("First_Name", "Gender", "Number_of_Children")
```

#### b. Summary and structure of 'df'
```{r babynames2}
summary(df)
str(df)
```

#### c. Find and display the misspelled record that ends with 'yyy'
```{r babynames3}
grep("yyy$",df$First_Name)
df[211,]
```

#### d. Remove the observation with the misspelled name and assign the remanining dataset to an object 'y2016'
```{r babynames4}
y2016 <- df[-211,]
```

## Question 2
### Data Merging

#### a. Import 'yob2015.txt' file and assign the dataset to an object 'y2015', rename column names
```{r babynames5}
y2015 <- read.table("/Users/swee/Desktop/SMU/Summer 2018/MSDS 6306 - Doing DS/dataset/yob2015.txt", sep= ",", header = FALSE)
colnames(y2015) <- c("First_Name", "Gender", "Number_of_Children")
```

#### b. Display the last ten rows of the dataframe, 'y2015'
```{r babynames6}
tail(y2015,10)
```

The last ten rows contain all male first names that begin with 'Z' and there are five children for each given name. 

#### c. Merge 'y2016' and 'y2015' by 'First Name' column and assign it to an object 'final'. Then check to confirm that there is no NA values in both "Number_of_Children" columns 
```{r babynames7}
final <- merge(y2016,y2015, by="First_Name")
colSums(is.na(final))
```

## Question 3
### Data Summary

#### a. Sum the amount of children in 2015 and 2016, and assign it to a column name called 'Total'
```{r babynames9}
final$Total <- final$Number_of_Children.x + final$Number_of_Children.y
```

#### b. Sort the data by 'Total' column and display the top 10 most popular names
```{r babynames10}
sort_data <- final[order(-final$Total),]
top10 <- sort_data[c(1:10),]
top10
```

#### c. Subset the dataset to contain only those with girl names and display the top 10 most popular girl names
```{r babynames11}
girl_names <- sort_data[ which(sort_data$Gender.x == 'F'), ]
top10_girls <- girl_names[c(1:10), c(1,6)]
top10_girls
```

#### d. Write the top 10 girl names and their totals to a csv file 
```{r babynames12}
write.csv(top10_girls, file = "top_ten_girl_names.csv", row.names = FALSE)
```

## Question 4
### CodeBook
#### A repository on GitHub for SMU MSDS Homework

GitHub link: https://github.com/sweechew91/SMU-MSDS-6306


